---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r loaddata, echo=TRUE}
setwd("C:/EMC/Education/Data_Science/Reproducible Research/Project1")
unzip("./RepData_PeerAssessment1/activity.zip",exdir = "./RepData_PeerAssessment1") 
activities <- read.csv("./RepData_PeerAssessment1/activity.csv", header = TRUE, na.strings="NA")
```

## Question 1: What is mean total number of steps taken per day?
```{r histogram, echo=TRUE}
#install.packages("dplyr")
library(dplyr)
days <- group_by(activities, date)
Summa <- summarize(days, steps = sum(steps, na.rm=TRUE))
Summa$daynum <- as.numeric(Summa$date)
barplot(Summa$steps, Summa$daynum, names.arg= Summa$daynum, ylab="Total steps number per day", xlab="day number")
summary(Summa)
```
Mean total number of steps taken per day is 9354;
Median total number of steps taken per day is 10395

## Question 2: What is the average daily activity pattern?
```{r dailyaverage, echo=TRUE}
intervals <- group_by(activities, interval)
avg <- summarize(intervals, steps = mean(steps, na.rm=TRUE))
plot(avg$interval, avg$steps, type="l", xlab="5-min interval", ylab="Average Steps")
summary(avg)
filter(avg,steps==max(steps))
```
The "5-minute interval", on average across all the days containing the maximum number of steps is "835": hh:mm 13:55.

## Question 3: Imputing missing values
```{r missingval1, echo=TRUE}
summary(activities)
```
NA values are 2304

```{r missingval2-3, echo=TRUE}
activities$steps[is.na(activities$steps)] <- mean(avg$steps)
```
NA values are now substituted by mean steps value per day

```{r missingval4, echo=TRUE}
SummawNA <- summarize(days, steps = sum(steps))
SummawNA$daynum <- as.numeric(SummawNA$date)
barplot(SummawNA$steps, SummawNA$daynum, names.arg= SummawNA$daynum, ylab="Total steps number per day", xlab="day number")
summary(SummawNA)
```
Mean total number of steps taken per day (including NAs) is 10765;
Median total number of steps taken per day (including NAs) is 10766
Both Mean and Median values are greater than without NAs



## Are there differences in activity patterns between weekdays and weekends?
No time...